---
title: "prepare_datasets"
output: default
---

```{r}
library(readxl)
library(writexl)
library(dplyr)
library(tidyverse)
library(countrycode)
library(readr)
library(haven)
library(lme4)
library(mediation)
```


# Load and prepare the datasets from different sources

## World Bank
### GDP data
```{r}
data_world_bank <- read_xlsx("public_data/GDP_World_Bank.xlsx", na = "..") %>% 
  transmute(
          year = `Time`,
          country_name = `Country Name`,
          country_code = `Country Code`,
          gdp = `GDP per capita, PPP (constant 2017 international $) [NY.GDP.PCAP.PP.KD]`)
          #gdp_mer = `GDP per capita (constant 2015 US$) [NY.GDP.PCAP.KD]`,
          #) 
```

calculate compound annual growth rate
```{r}
time_span=3

data_gdp <- 
  data_world_bank %>% 
  group_by(country_code) %>% 
  arrange(year) %>% 
  dplyr::mutate(gdp_old =  lag(gdp,time_span), growth = ((gdp / gdp_old)^(1/ time_span) - 1)*100) %>% 
  dplyr::select(year, country_name, country_code, gdp, growth) %>% 
  ungroup()
```

### Inequality
```{r}
data_world_bank_inequality <- read_xlsx("public_data/Inequality_World_Bank.xlsx", na = "..") %>% 
  transmute(
          year = `Time`,
          country_code = `Country Code`,
          gini = `Gini index [SI.POV.GINI]`)
           
```



## World Value Survey
Importance to be rich
```{r}
wvs_5 <- 
  read_xlsx("public_data/importance_rich_WVS_wave_5.xlsx", skip=6) %>% 
  filter(...1 == "Mean") %>% 
  dplyr::select(!c(...2, ...1)) %>% 
  pivot_longer(everything(),names_to="country_name", values_to = "importance_rich") %>% 
  transmute(country_code = countrycode(country_name, origin='country.name', destination = 'iso3c'), importance_rich_5 = 7-importance_rich) # change ordering of values such as low values correspond to low importance and high values to high importance of being rich

wvs_6 <- 
  read_xlsx("public_data/importance_rich_WVS_wave_6.xlsx", skip=6) %>% 
  filter(...1 == "Mean") %>% 
  dplyr::select(!c(...2, ...1)) %>% 
  pivot_longer(everything(),names_to="country_name", values_to = "importance_rich") %>% 
  transmute(country_code = countrycode(country_name, origin='country.name', destination = 'iso3c'), importance_rich_6 = 7-importance_rich)
```

join two waves

```{r}
data_wvs <- 
  full_join(wvs_5,wvs_6, by= "country_code") %>% 
  rowwise() %>% 
  transmute(country_code, importance_rich = mean(c_across(c("importance_rich_5", "importance_rich_6")), na.rm=TRUE))
```




## World Governance Indicators
Voice and accountability, Government effectiveness


```{r}
# the data is formatted in a messy way with a multiple row header, which is why we have to handle it first
data_head <- read_xlsx("public_data/world_governance_indicators.xlsx", 
                      n_max = 2, 
                      col_names = FALSE, 
                      skip= 13,
                      sheet = "VoiceandAccountability")

new_names <- data_head %>%
  summarise(across(.fns = paste, collapse = "_")) %>%
  unlist() %>% unname()


data_WGI_democracy <- 
  read_xlsx("public_data/world_governance_indicators.xlsx", 
                      col_names = new_names, 
                      skip= 15,
                      sheet = "VoiceandAccountability") %>% 
  rename(country_code = "NA_Code", country_name = "NA_Country/Territory") %>% 
  mutate(across(3:last_col(), ~as.numeric(.))) %>% 
  # make a row for each data column
  pivot_longer(
    cols = -c(country_name, country_code), 
    names_to = c("year", "type"),
    names_sep = "_",
    names_transform = list(year = as.integer),
    values_to = "democracy"
  ) %>%
  filter(type=="Estimate") %>% 
  dplyr::select(country_code, year, democracy)

data_WGI_government_effectiveness <- 
  read_xlsx("public_data/world_governance_indicators.xlsx", 
                      col_names = new_names, 
                      skip= 15,
                      sheet = "GovernmentEffectiveness") %>% 
  rename(country_code = "NA_Code", country_name = "NA_Country/Territory") %>% 
  mutate(across(3:last_col(), ~as.numeric(.))) %>% 
  # make a row for each data column
  pivot_longer(
    cols = -c(country_name, country_code), 
    names_to = c("year", "type"),
    names_sep = "_",
    names_transform = list(year = as.integer),
    values_to = "government_effectiveness"
  ) %>%
  filter(type=="Estimate") %>% 
  dplyr::select(country_code, year, government_effectiveness)

```


## ILO
Social protection effective coverage
```{r}
data_ILO <- 
  read_csv("public_data/social_protection_coverage_ILO.csv") %>% 
  transmute(country_code = ref_area, year=time, social_protection=obs_value) %>% 
  group_by(country_code) %>% 
  summarise(social_protection = mean(social_protection)) %>% 
  ungroup() 
  #filter(!startsWith(country_code,"X"))
```


## Comparative Welfare Entitlements Dataset 
Welfare state generosity index

```{r}
data_welfare_state <- 
  read_xlsx("public_data/welfare_state_generosity_CWEP.xlsx") %>% 
  transmute(country_code = COUNTRYABBREV, year=YEAR, welfare_state = TOT_GEN) %>% 
  drop_na()
```



## Gallup World Poll

```{r}
data_Gallup <- 
  read_dta("path-to-Gallup-data.dta",
           col_select = c(WPID_RANDOM,
                          wgt, 
                          YEAR_CALENDAR, 
                          countrynew,
                          WP7572,
                          WP16,
                          WP4656,
                          WP63,
                          WP67,
                          WP69,
                          WP70,
                          WP71,
                          WP74,
                          WP1219,
                          WP1220,
                          WP1223,
                          WP40,
                          WP43,
                          WP23,
                          WP95,
                          WP94,
                          WP97,
                          WP117,
                          WP118,
                          WP113,
                          WP27,
                          WP61,
                          WP3117,
                          WP65,
                          WP60,
                          EMP_2010,
                          WP134,
                          INCOME_4,
                          INCOME_2,
                          INCOME_1,
                          INCOME_3,
                          INCOME_7,
                          WP1233,
                          WP119,
                          WP108,
                          WP109,
                          WP110,
                          WP19472,
                          WP137,
                          WP138,
                          WP139,
                          WP141,
                          WP88,
                          WP30
                          )) %>% 
  transmute(id = WPID_RANDOM,
            weight = wgt, 
            year = YEAR_CALENDAR,
            country_name = countrynew,
            country_code = countrycode(countrynew, origin='country.name', 
                                       destination = 'iso3c'),
            urban_rural = WP7572,
            life_evaluation = case_match(WP16,0~0,1~1,2~2,3~3,4~4,5~5,6~6,7~7,8~8,9~9,10~10),
            life_satisfaction = case_match(WP4656,0~0,1~1,2~2,3~3,4~4,5~5,6~6,7~7,8~8,9~9,10~10),
            smile = case_match(WP63, 1 ~ 1, 2 ~ 0),
            enjoyment = case_match(WP67, 1 ~ 1, 2 ~ 0),
            no_worry = case_match(WP69, 1 ~ 0, 2 ~ 1),
            no_sadness = case_match(WP70, 1 ~ 0, 2 ~ 1),
            no_stress = case_match(WP71, 1 ~ 0, 2 ~ 1),
            no_anger = case_match(WP74, 1 ~ 0, 2 ~ 1),
            gender = factor(WP1219, levels = c(2,1), labels = c("female", "male")),
            age = WP1220,
            relationship_status =factor(WP1223, levels = c(1,2,3,4,5,8,6,7), 
                                        labels = c("single", "partnered", "separated", "separated", "widowed", "partnered"), exclude=c(6,7)),
            food = case_match(WP40, 1 ~ 0, 2 ~ 1),
            housing = case_match(WP43, 1 ~ 0, 2 ~ 1),
            health = case_match(WP23, 1 ~ 0, 2 ~ 1),
            water = case_match(WP95, 1 ~ 1, 2 ~ 0),
            air = case_match(WP94, 1 ~ 1, 2 ~ 0),
            healthcare = case_match(WP97, 1 ~ 1, 2 ~ 0),
            nothing_stolen = case_match(WP117, 1 ~ 0, 2 ~ 1),
            not_assaulted = case_match(WP118, 1 ~ 0, 2 ~ 1),
            safe_walking_alone = case_match(WP113, 1 ~ 1, 2 ~ 0),
            social_support = case_match(WP27, 1 ~ 1, 2 ~ 0),
            respect = case_match(WP61, 1 ~ 1, 2 ~ 0),
            education = case_match(WP3117, 1~0, 2~1, 3~1),
            interesting_activity = case_match(WP65, 1 ~ 1, 2 ~ 0),
            recreation = case_match(WP60, 1 ~ 1, 2 ~ 0),
            occupation = case_match(EMP_2010, 4~0, c(1,2,3,5,6)~1),
            freedom = case_match(WP134, 1 ~ 1, 2 ~ 0),
            personal_income = INCOME_4,
            household_income = INCOME_2,
            personal_income_local = INCOME_3,
            household_income_local = INCOME_1,
            imputed = INCOME_7,
            household_size = household_income/personal_income,
            religious_affiliation = factor(WP1233, levels = c(26,seq(0,25),28,29,97,98,99), labels = c("no", rep("yes",28)), exclude = c(97,98,99)),
            religion_important = factor(WP119, levels = c(2,1,3,4), labels = c("no", "yes"), exclude=c(3,4)),
            donated_money = case_match(WP108, 1 ~ 1, 2 ~ 0),
            volunteered = case_match(WP109, 1 ~ 1, 2 ~ 0),
            helped_stranger = case_match(WP110, 1 ~ 1, 2 ~ 0),
            rating_economic_conditions = case_match(WP19472, 1~1,2~2,3~3,4~4),
            confidence_military = case_match(WP137, 1 ~ 1, 2 ~ 0),
            confidence_courts = case_match(WP138, 1 ~ 1, 2 ~ 0),
            confidence_government = case_match(WP139, 1 ~ 1, 2 ~ 0),
            confidence_finance = case_match(WP141, 1 ~ 1, 2 ~ 0),
            expected_economic_conditions = case_match(WP88, 3 ~ -1, 2 ~0, 1 ~ 1), 
            satisfaction_standard_living = case_match(WP30, 1 ~ 1, 2 ~ 0)
            ) %>%
    filter(
    age != 100, 
  ) %>% 
  # build mean indices for multi-item measures
  mutate(positive_affect = rowMeans(pick(smile, enjoyment), na.rm=TRUE),
       absence_negative_affect = rowMeans(pick(no_worry, no_sadness, no_stress, no_anger), na.rm=TRUE),
       security = rowMeans(pick(nothing_stolen, not_assaulted, safe_walking_alone), na.rm=TRUE), # TODO: decide how to deal with missing values!
       security_obj = rowMeans(pick(nothing_stolen, not_assaulted), na.rm=TRUE),
       altruistic_behaviour = rowMeans(pick(donated_money, volunteered, helped_stranger), na.rm=TRUE),
       confidence_institutions = rowMeans(pick(confidence_military, confidence_courts, confidence_finance, confidence_government), na.rm=TRUE),
       ) %>% 
  # binarise security indices
  mutate(security = if_else(security==1, 1, 0),
         security_obj = if_else(security_obj==1, 1, 0)) %>% 
  # build religiosity
  unite("rel_paste", religious_affiliation:religion_important) %>% 
  mutate(religious = case_match(rel_paste, c("no_no", "no_yes") ~ "no", "yes_no" ~ "yes (formally)", "yes_yes" ~ "yes (practising)" )) %>% 
  # build country averages of need satisfaction with all data points available
  group_by(country_code, year) %>% 
  mutate(across(c(food, # build country averages
                  housing,
                  health,
                  water,
                  air,
                  healthcare,
                  security, 
                  security_obj,
                  social_support,
                  respect,
                  education,
                  interesting_activity,
                  recreation,
                  occupation,
                  freedom),
                ~ 100*weighted.mean(., weight, na.rm = TRUE), .names = "country_average_{.col}")
         ) %>% 
  ungroup() %>% 
  # kick out data points that are certainly not usable (country or year not known)
  drop_na(country_code, year) %>% 
  # remove data points from Somalia, South Sudan, or with zero income
  filter(!(country_name %in% c("Somalia", "South Sudan") | personal_income == 0)) %>% 
  # build relative income measures
  group_by(country_code, year) %>% 
  mutate(relative_income = ecdf(personal_income)(personal_income) * 100,
         relative_income_median_ratio = personal_income/median(personal_income),
         relative_income_stand = (personal_income-mean(personal_income))/sd(personal_income),
         relative_income_stand_median = (personal_income-median(personal_income, na.rm = TRUE))/mad(personal_income, na.rm = TRUE),
         ) %>% 
  ungroup() %>%
  dplyr::select(-country_name)
 


```


# Combine into one big dataset

```{r}

data_all <- 
  data_gdp %>% 
  full_join(data_world_bank_inequality, by = join_by("country_code", year)) %>% 
  full_join(data_wvs, by = "country_code") %>% 
  full_join(data_WGI_government_effectiveness, by = join_by("country_code", year)) %>% 
  full_join(data_WGI_democracy, by = join_by("country_code", year)) %>% 
  full_join(data_ILO, by = join_by("country_code")) %>% 
  full_join(data_welfare_state, by = join_by("country_code", year)) %>% 
  right_join(data_Gallup, by = join_by("country_code", year)) %>% 
  unite("country_year", c(country_name, year), remove = FALSE) %>% 
  # log-transformation of income and GDP; build age squared
  mutate(personal_income = log(personal_income), #TODO: determine good shift values in case we decide to include zero income values
         gdp = log(gdp),
         age_squared = age^2) %>% 
  dplyr::select(id,
            weight,
            year,
            country_code,
            country_name,
            country_year,
            life_evaluation,
            life_satisfaction,
            positive_affect,
            absence_negative_affect,
            gender,
            age,
            age_squared, 
            relationship_status,
            food,
            housing,
            health,
            water,
            air,
            healthcare,
            security, 
            security_obj,
            social_support,
            respect,
            education,
            interesting_activity,
            recreation,
            occupation,
            freedom,
            personal_income,
            relative_income,
            country_average_food,
            country_average_housing,
            country_average_health,
            country_average_water,
            country_average_air,
            country_average_healthcare,
            country_average_security, 
            country_average_security_obj,
            country_average_social_support,
            country_average_respect,
            country_average_education,
            country_average_interesting_activity,
            country_average_recreation,
            country_average_occupation,
            country_average_freedom,
            gdp,
            growth,
            personal_income,
            relative_income,
            social_protection,
            welfare_state,
            government_effectiveness,
            democracy,
            importance_rich,
            religious,
            altruistic_behaviour,
            rating_economic_conditions,
            confidence_institutions,
            expected_economic_conditions,
            satisfaction_standard_living, 
            gini
  )


write_csv(data_all,"data_all.csv")


```

for reading the dataset, some variables need to be retransformed into factors as this information is not saved in the csv format:
```{r}
data_all_test <- readr::read_csv("data_all.csv", 
                                 col_types = "idicccddddcddciiiiiiddiiiiiiiddddddddddddddddddddddddcddddid") %>% 
  mutate(across(
    c(year,
      gender,
      relationship_status,
      food,
      housing,
      health,
      water,
      air,
      healthcare,
      security,
      security_obj,
      social_support,
      respect,
      education,
      interesting_activity,
      recreation,
      occupation,
      freedom,
      religious
      ), ~ factor(.)), religious = relevel(relevel(religious, "yes (formally)"), "no"), relationship_status = relevel(relationship_status, "single"))
```


